Done

### 2024-05-15 done.qmd
update

@@

@@

@@

>>>>

## 2024

2024 onwards: member of University of Sheffield Research Culture Steering Board, which provides leadership and coordination for the development of institutional research culture.

2021 to 2024: member of University of Sheffield Research Excellence Working group, which developed, consulted on and agreed a common definition and understanding of ‘excellence’ for use alongside the institutional research strategy.

@@

2021 onwards: member, University of Sheffield Open Research Advsory Group, "providing strategic leadership in the ongoing development, promotion and implementation of the policies and practices supporting the University’s
commitment to Open Research"

@@

2020 onwards: member, University Vice President for Research's Strategy Group (VPSG)

@@

2017 to 2021: member, University of Sheffield Open Access Advisory Group, representing Faculty of Science, providing strategic overview of scholarly communication
